%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Saurabh}{Verma}{ \urlstyle{same}\href{https://saurabh0vipin.github.io/}{saurabh0vipin.github.io}\\
\href{mailto:saurabhvipin55@gmail.com}{saurabhvipin55@gmail.com} | (+91) 7839452567
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NIT SRINAGAR}
\descript{BTech in Information \\
Technology}
\location{July 2016-Present | (Final Year)}
\location{ CGPA: 8.73 / 10.0 (Till 6th sem)}
\sectionsep

\subsection{RLB Memorial School}
\descript{XII (Science + Maths) | CBSE}
\location{June 2013-April 2015 | Lucknow, UP}
\location{Score: 467/500 | 93.40\%}
\sectionsep

\subsection{RLB Memorial School}
\descript{X (Secondary School) | CBSE}
\location{June 2011-April 2013 | Lucknow, UP}
\location{CGPA: 10.0/10.0 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/saurabh0vipin}{\bf saurabh0vipin} \\
LinkedIn://  \href{https://www.linkedin.com/in/saurabh-verma-970117156/}{\bf Saurabh-Verma} \\
Stack Overflow://  \href{https://stackoverflow.com/users/10853514/saurabh-verma}{\bf Saurabh-Verma} \\
InterviewBit:// \href{https://www.interviewbit.com/profile/saurabh_vipin}{\bf saurabh\_vipin} \\
CodeChef:// \href{https://www.codechef.com/users/saurabh_vipin}{\bf saurabh\_vipin} \\
HackerEarth:// \href{https://www.hackerearth.com/@Saurabh_vipin}{\bf saurabh\_vipin} \\
Codeforces:// \href{http://codeforces.com/profile/saurabh.vipin}{\bf saurabh.vipin} \\
Hackerrank:// \href{https://www.hackerrank.com/Saurabh_vipin}{\bf saurabh\_vipin} \\ 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Data Structures \\
Algorithms \\
Database Management System \\
Operating System \\
Object-Oriented Programming \\
Java Programming \\
Artificial Intelligence \\
Web Designing \\
Mathematics for Computer Science \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\textbullet{}Data Structures  \textbullet{}Algorithms \\ \textbullet{}C  \textbullet{}C++ \textbullet{}Github \textbullet{}\LaTeX  \\
\textbullet{}Java \textbullet{}JavaScipt \textbullet{} MySQL \\
\location{Familiar:}
\textbullet{}Python  \textbullet{}Bash Scripting \textbullet{}HTML \\
\textbullet{}CSS \textbullet{}JQuery \textbullet{}MATLAB  \\
\textbullet{}Linux(Ubuntu)     \textbullet{}RegEx \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Centre for Artificial Intelligence and Robotics}
\descript{| Research Intern }
\location{Dec 2018 - Feb 2019 | DRDO, Bengaluru}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on Defence Live Data for Various Entity Extraction such as OfficerRank, REGIMENT, etc.
\item Led and shipped Yoda - the admin interface for the new Phoenix platform. 
\item Full-stack developer - Wrote and reviewed code for JS using Backbone, Jade, Stylus and Require and Scala using Play
\end{tightemize}
\sectionsep

\runsubsection{ALT Center}
\descript{| Intern }
\location{July 2018 - Aug 2018 | Ghaziabad, UP}
\begin{tightemize}
\item Designed a secured Network Architecture with different types of Datagram Packet Filters on Routers.
\item Used standard and extended ACL to filter out HTTP and FTP traffic of undesired users.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Digital Data Encoder}
\descript{}
\location{Sept 2018 – Oct 2018}
\begin{tightemize}
\item Encodes Binary Data into Digital Signals.
\item Implemented Line coding (NRZ-L, NRZ-I, Manchester, Differential Manchester, AMI) encoder and scrambler (B8ZS, HDB3) with Random digital data generator. 
\end{tightemize}
\sectionsep

\runsubsection{Text Editor}
\descript{}
\location{June 2018 – June 2018}
\begin{tightemize}
\item Designed Text Editor functions using Two stacks Model.
\item Applied C++ Object Oriented Programming and STL Concepts.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Competitive Programming} 
\begin{tabular}{rll}
2020	     & 122/6504  & Codathon - Inter NIT Coding Competition\\
2020         & 867/17532  & Codeforces Round \#615 \\
2019	     & Top 200/1,18,000  & HackWithInfy 2019-Infosys All India Coding Challenge\\
2019	     &93/2765   & CodersBit'19 | InterviewBit\\
2019         & 514/55654 & CodeVita-Season 8  \\
2019         & 239/10424 &  July Challenge 2019 | Codechef\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements \& Awards} 
\subsection{}
\begin{tightemize}
\item  Winner of \textbf{Code Relay} event organized in \textbf{Exordium 2.0}
\item  Runner Up of \textbf{Code Jumble} event organized in \textbf{Techvaganza'19}.
\item Rank Holder, among top 5 in IT Branch.
\item Medal for full Attendance in two consecutive academic years.
\end{tightemize}
\end{minipage} 
\end{document}  \documentclass[]{article}
